Figures to insert in text

### 2018-03-14 Chapters/Chapter02.tex
little garibation on conclusion...

\section{Future work}

@@

\subsection{Multiple levels}

Deep neural networks, alphaGo, alphazero

\subsection{i versus l}

\subsection{Magic numbers}

@@

\subsection{Classification with context using sequences --- for words instead of only letters}

\subsection{Symmetrical, rapidly accessible, Hard Locations}

@@

\section{Seeing farther}

@@

If

We have generated a Docker image, which makes it even easier to explore the framework. After running the container, a Jupyter Notebook is available with sdm-framework and other tools already installed.

All the simulations and graphics generated in this thesis are promptly available to be re-executed and explored by those interested. We invite readers to take a look and explore a little bit.

@@

Of course, for the skeptical reader who may consider software a less worthy pursuit, there is also new work here.  The mathematics of the model has been shown to be correct numerically (with a single, small, anomaly); we have shown how to execute unsupervised learning with nothing besides operations original to the SDM; we have studied the generalized Murilo read; we have seen noise filtering; the death of neurons; how information-theory may be of use; and finally, we have reproduced numerous of the original propositions put forth by Kanerva.  The emphasis might have been on \emph{breadth of topics}, in detriment of depth here or there.  But this is due to our research group's enthusiam for the topic; we do indeed believe that SDM is --- if not correct --- extremely close to a full scientific understanding of human long-term memory.  If so, it is such a monumental achievement that we want readers to be able to see all of what we see and imagine the vastness of possibilities.  The work on, say, reinforcement learning, is most definitely not the definitive work we will see on the subject, but a challenge left for readers to contemplate. Ralph Waldo Emerson once said \emph{Do not go where the path may lead. Go, instead, where there is no path, and leave a trail.}  Dr. Kanerva has left the trail.  It is my job to pave it and to throw light at it and to try to deliver an easier pathway for the next generation.  Some essays completely shut the door close at the end; this one intends to leave it wide open. As the reader might have noticed, this final section does not read as an analysis of the work done; it reads, instead, as a \emph{desiderata}, a prologue, a yearning for others to join me in imagining the shape of things to come.

>>>>

@@

% \subsection{Multiple levels}

% Deep neural networks, alphaGo, alphazero

% \subsection{i versus l}

\section{Magic numbers}

@@

% \subsection{Classification with context using sequences --- for words instead of only letters}

\section{Symmetrical, rapidly accessible, Hard Locations}

@@

\section{Paving and illuminating the pathway}

@@

All the simulations and graphics generated in this thesis are promptly available to be re-executed and explored by those interested. We have generated a Docker image, which makes it even easier to explore the framework. After running the container, a Jupyter Notebook is available with sdm-framework and other tools already installed. We invite the reader to take a look and explore a little bit.

@@

Of course, for the skeptical reader who may consider software a less worthy pursuit, there is also new work here.  The mathematics of the model has been shown to be correct numerically (with a single, small, anomaly); we have shown how to execute unsupervised learning with nothing besides operations original to the SDM; we have studied the generalized Murilo read; we have seen noise filtering; the death of neurons; how information-theory may be of use; and finally, we have reproduced numerous of the original propositions put forth by Kanerva.  The emphasis might have been on \emph{breadth of topics}, in detriment of depth here or there.  But this is due to our research group's enthusiam for the topic; we do indeed believe that SDM is --- if not correct --- extremely close to a full scientific understanding of human long-term memory.  If so, it is such a monumental achievement that we want readers to be able to see all of what we see and imagine the vastness of possibilities.  The work on, say, reinforcement learning, is most definitely not the definitive work we will see on the subject, but a challenge left for readers to contemplate. Ralph Waldo Emerson once said \emph{Do not go where the path may lead. Go, instead, where there is no path, and leave a trail.}  Dr. Kanerva has left the trail.  It is my job to pave it and illuminate it and to try to deliver an easier pathway for the next generation.  Some essays completely shut the door close at the end; this one intends to leave it wide open. As the reader might have noticed, this final section does not read as an analysis of the work done; it reads, instead, as a \emph{desiderata}, a prologue, a yearning for others to join me in imagining the shape of things to come.

### 2018-03-14 Chapters/sdm-applications.tex
little garibation on conclusion...

\subsection{Training}

@@

\subsection{Results}

@@

When playing against mixed players, SDM has also adapted. In Figure \ref{fig:ttt-results-mixed}, it has played 6,000 games against random player, smart player, and another SDM player. In each cycle, one of them was randomly chosen. The number of loses over time is decreasing, while the number of wins and draws change a lot. It is easy to notice when the other SDM player was chosen, because all games in that cycle have draw.

\begin{figure}[!htb]
\centering
\subfloat[Loses over time]{\includegraphics[width=\textwidth]{./images02/ttt/results-random-loses.png}}

@@

\begin{figure}[!htb]
\centering
\subfloat[Loses over time]{\includegraphics[width=\textwidth]{./images02/ttt/results-smart-loses.png}}

@@

\begin{figure}[!htb]
\centering
\subfloat[Loses over time]{\includegraphics[width=\textwidth]{./images02/ttt/results-sdm-loses.png}}

@@

\begin{figure}[!htb]
\centering
\subfloat[Loses over time]{\includegraphics[width=\textwidth]{./images02/ttt/results-mixed-loses.png}}

>>>>

\section{Training}

@@

\section{Results}

@@

When playing against mixed players, SDM has also adapted. In Figure \ref{fig:ttt-results-mixed}, it has played 6,000 games against random player, smart player, and another SDM player. In each cycle, one of them was randomly chosen. The number of losses over time is decreasing, whereas the number of wins and draws change a lot. It is easy to notice when the other SDM player was chosen, because all games in that cycle have draw.

\begin{figure}[!htb]
\centering
\subfloat[Losses over time]{\includegraphics[width=\textwidth]{./images02/ttt/results-random-loses.png}}

@@

\begin{figure}[!htb]
\centering
\subfloat[Losses over time]{\includegraphics[width=\textwidth]{./images02/ttt/results-smart-loses.png}}

@@

\begin{figure}[!htb]
\centering
\subfloat[Losses over time]{\includegraphics[width=\textwidth]{./images02/ttt/results-sdm-loses.png}}

@@

\begin{figure}[!htb]
\centering
\subfloat[Losses over time]{\includegraphics[width=\textwidth]{./images02/ttt/results-mixed-loses.png}}
